R Notebook

### 2022-12-19 data/v1b-analysis.rmd
Update analysis

attemps <- events %>%
  filter(participant_id %in% completed) %>% 
  filter(event_name == "attempts")

@@

ggsave("r2-data.pdf", device = "pdf", plot = last_plot(), units ="mm", width = 210)

@@

r <- wilcox.test(d$Chameleon, d$Ghc, paired=TRUE)
r
```

@@

```{r}
events |>
  ggplot(mapping=aes(x=time)) +
  geom_density()

>>>>

# 
# attemps <- events %>%
#   filter(participant_id %in% completed) %>% 
#   filter(event_name == "attempts")

@@

# ggsave("r2-data.pdf", device = "pdf", plot = last_plot(), units ="mm", width = 210)

@@

shapiro.test(durations$duration)
t.test(d$Chameleon, d$Ghc, paired = TRUE, alternative = "two.sided")

# r <- wilcox.test(d$Chameleon, d$Ghc, paired=TRUE)
# r
```

@@

```{r}
```

```{r}
events |>
  ggplot(mapping=aes(x=time)) +
  geom_density()
```

```{r}
durations |> 
durations |> 
  ggplot(mapping=aes(duration)) +
